%
%---------------------------------
%   PACKAGES AND CONFIGURATIONS
%---------------------------------

\documentclass{resume}

\usepackage[left=0.5 in,top=0.3in,right=0.5 in,bottom=0.3in]{geometry} % Margins
\usepackage{amssymb}
\usepackage{chemformula}

\name{Armando Arevalo} % Name
\address{\Large a.arevalo3e8@gmail.com \\ \Large (619) 713-8214 \\ \Large Rancho Cucamonga, CA}  % Email, phone number, and location

%---------------------------------------------------------------------------------
%   START OF DOCUMENT
%---------------------------------------------------------------------------------

\begin{document}

%--------------------
%	WORK EXPERIENCE
%--------------------

\begin{Section}{Work Experience}

%-------------------
%   InCyle Section
%-------------------

\begin{workSection} {InCylce Software Inc}{Aug. 2022}{Feb. 2023}{Data Science Intern}{Remote}

\item My project comprised building a dashboard for company sales data to inform sales team on: deal velocity through sales pipeline, likelihood-to-close successfully, and high-touch/low-touch client interaction to redirect efforts. 
\item Using \textbf{Azure Databricks} to perform EDA, preprocess raw data, anonymize sensitive information to prevent data leakage risks, calculate deal velocity and rolling-mean velocity, apply Naïve Bayes ML algorithms to build models to predict likelihood-to-close at each step in sales pipeline, leverage temporal features to classify deals as high or low touch, organize trained models and notebook’s input and output data in well-structured Delta table folder system. 
\item Design a \textbf{Power BI} dashboard having charts and tables that summarize deployed processed data, at both all-deals level and single-deal level, integrating drill-through capabilities. 
\item Using \textbf{Azure Data Factory} to automate processing and deployment of new data to dashboard each week utilizing an orchestration pipeline that triggers when new data is available, finalizing by sending Outlook notifications upon successful execution.
\item Use Azure DevOps to track weekly progress, use repos to backup code, and document project with schematics in MS Visio and workflow outlines in Markdown.

\end{workSection}

%-------------------------
%   Analytis Lab Section
%-------------------------
\begin{workSection}{James Analytis Condensed Matter Physics Lab, at UC Berkeley}{Jan. 2020}{Aug. 2021}{Undergraduate Researcher}{Berkeley, CA}

 \item  Prepare \ch{RuCl3} crystal samples for analysis by grinding and using microscope to achieve micron-level thickness, masking samples with resin to coat gold injector-detector contacts, and soldering wiring to sample contacts.
 \item In Jupyter notebooks, create visuals for simple 2D diffusion simulations using PDE numerical methods with varying initial and Dirichlet-Neumann boundary conditions using Python.
 \item Use COMSOL Multiphysics to design 2D magnon diffusion simulations in a magnetic insulator (\ch{YIG}) by injecting spin via Spin Hall Effect for various initial and boundary conditions.
 \item \textbf{Extensive} research, summarization, and presenting on successful literature to give direction for research.

\end{workSection}

\end{Section}

%----------------------
%	EDUCATION SECTION
%----------------------
\begin{Section}{Education}

%-----------------
%   UC Berkeley
%-----------------

\begin{eduSection}{University of California, Berkeley}{May 2021}{B.A., Physics}{Berkeley, CA}
\item \textbf{GPA: 3.59 / 4.0}; \textit{Cum Laude}, Regents’ and Chancellor’s Scholarship
\end{eduSection}

%---------------------
%   Cuyamaca College
%---------------------

\begin{eduSection}{Cuyamaca College}{May 2019}{A.A., Physics; A.A., Mathematics; A.A., University Studies - Science and Mathematics}{Rancho San Diego, CA}
 \item \textbf{GPA: 3.94/4.0}; President’s Honor List; Phi Theta Kappa Honors Society, Omicron Chapter (\textit{President}); STEM Club (\textit{Senator}); Physics Tutor 
\end{eduSection}

\end{Section}

%------------------------------------------------
%   CERTIFICATIONS, SKILLS \& INTERESTS SECTION
%------------------------------------------------

\begin{Section}{CERTIFICATIONS, SKILLS \& INTERESTS}

\begin{csiSection}{Microsoft Certified Azure Data Scientist Associate, AWS Certified Cloud Practitioner}{analytical, critical and abstract thinking; problem solving; data processing, analysis and visualization; statistical analysis; machine learning; advanced mathematics; advanced physics; literature reviews; project documentation; research skills; presentation skills; reading comprehension; technical writing; \textbf{Azure:} DevOps, Databricks, Machine Learning, and Data Factory; Power BI; GitHub; LaTex; Python; PySpark}{Listening to music; running, swimming, and hiking; reading e-books; watching movies; playing guitar}
\end{csiSection}

\end{Section}

%--------------------
%   FOOTNOTE LINKS
%--------------------

\hfil \blfootnote{\footnotesize \textcolor{gray}{\textit{LinkedIn: http://www.linkedin.com/in/armando-arevalo-7042041ab; GitHub: https://github.com/a-arev}}} \hfil


%---------------------------------------------------------------------------------
%   END OF DOCUMENT
%---------------------------------------------------------------------------------

\end{document}

